Edge sign prediction in general graphs and Correlation Clustering

### 2017-10-16 edge/experiments.tex
reorganize the model material

Now that we have a direction $w_{uv} \in \mathcal{D}_k$ assigned to every edge $(u,v)$, we want to
find a set of user profiles $X=\{x_u\}_{u\in V}$ that maximize the edge score and minimize the node
loss, defined respectively by equations \eqref{eq:edge_full}\stodo{not really} and \eqref{} in the
previous section as:
\begin{align*}
  \mathcal{L}_{\mathrm{edge}} &=
  \sum_{u,v \in E} \left(x_u \circ x_v\right)^T w_{uv} \quad \text{and} \\
  \mathcal{L}_{\mathrm{node}} &=
  \sum_{u\in V} \left|\left| x_u - b_u - \sum_{v \in \nei(u)} a_{uv} w_{uv} \right|\right|^2\,,
\end{align*}
where for simplicity, we fix $b_u = \zerov$ and $a_{uv} = 1$. Furthermore, to ensure that the
assigned direction of any edge $(u,v)$ achieve a better score than the other directions (that is
$\forall w_\ell \in \mathcal{D}_k \setminus \{w_{uv}\}\,, {s_{uv}}^T w_{uv} \geq  {s_{uv}}^T
w_\ell$) we also minimize cross-entropy loss commonly used in non-binary classification
problem~\autocite[Section 4.3.4]{PRML06}.  Specifically, recall that the goodness of direction
$w_\ell$ for the edge $(u,v)$ is $g(s_{uv}, w_{uv})$. If we denote by $p_{uv,\ell} = \frac{\exp
\left( g(s_{uv}, w_{uv}) \right)}{\sum_{\ell=1}^k \exp \left( g(s_{uv}, w_\ell) \right)}$ the
softmax \enquote{probability} of $s_{uv}$ being explained by direction $\ell$, the cross-entropy
loss is defined by
\begin{equation*}
  \mathcal{L}_{\mathrm{cross-entropy}} = -\sum_{u,v \in E} \sum_{l=1}^k
  \Ind{w_{uv} = w_\ell} p_{uv,\ell}
\end{equation*}

>>>>

Now that we have a direction $w_{uv} \in \mathcal{D}_k$ assigned to every edge $(u,v)$, we want to
find a set of user profiles $X=\{x_u\}_{u\in V}$ that maximize the edge score and minimize the node
loss, defined respectively by equations \eqref{eq:edge_full} and
\eqref{eq:edge_node_loss} in the previous section as:
\begin{align*}
  \mathcal{L}_{\mathrm{edge}} &=
  \sum_{u,v \in E} \left(x_u \circ x_v\right)^T w_{uv} \quad \text{and} \\
  \mathcal{L}_{\mathrm{node}} &=
  \sum_{u\in V} \left|\left| x_u - b_u - \sum_{v \in \nei(u)} a_{uv} w_{uv} \right|\right|^2\,,
\end{align*}
where for simplicity, we fix $b_u = \zerov$ and $a_{uv} = 1$. Furthermore, to ensure that the
assigned direction of any edge $(u,v)$ achieve a better score than the other directions (that is
$\forall w_\ell \in \mathcal{D}_k \setminus \{w_{uv}\}\,, {s_{uv}}^T w_{uv} \geq  {s_{uv}}^T
w_\ell$) we also minimize cross-entropy loss commonly used in non-binary classification
problem~\autocite[Section 4.3.4]{PRML06}.  Specifically, recall that the goodness of direction
$w_\ell$ for the edge $(u,v)$ is $g(s_{uv}, w_{uv})$. If we denote by $p_{uv,\ell} = \frac{\exp
\left( g(s_{uv}, w_{uv}) \right)}{\sum_{\ell=1}^k \exp \left( g(s_{uv}, w_\ell) \right)}$ the
softmax \enquote{probability} of $s_{uv}$ being explained by direction $\ell$, the cross-entropy
loss is defined by
\begin{equation*}
  \mathcal{L}_{\mathrm{cross-entropy}} = -\sum_{u,v \in E} \sum_{l=1}^k
  \Ind{w_{uv} = w_\ell} p_{uv,\ell}
\end{equation*}
